The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-07-07 manuscript.Rmd
more manuscript edits

Similarly, a significant fraction of museum records have missing or inaccurate geographic information associated with them. While tools have been developed to convert names of locales into GPS coordinates on land [@rios2010geolocate], similar approaches may not work for locales at sea. However, geographic information is available in other forms, and can be digitized.

For both the spelling of scientific names, and the geographic information, computing tools can be developed to detect issues and propose solutions. There are opportunities to develop computing services that use publicly available data to flag and fix these issues directly in collection databases. It however requires that resources are made available to museum collections to address these issues.

Increasing the computing literacy of the staff of museums in order for them to manipulate and use the data from their collection database is equally critical. As data across institutions get pooled into the large biodiversity information systems, it is crucial that data standards such as Darwin Core are embraced by the community.

Another venue to improve the quality of the data in biodiversity information systems, is better incitives from journal editors and funding agencies for scientists to publish their occurrence records in databases alongside their papers as it is done for genetic data with GenBank [@Huang2011e].

Specimens with accurate identifications and specimens that have been preserved in conditions such that it is possible to get DNA out of them should be prioritized, as they yield the most data that are relevant to biodiversity knowledge.

@@

This study highlights that we have too little data about too few species of marine invertebrates. We recommend that additional coordinated field expeditions are organized to sample more thoroughly the marine environment. The relation between sampling effort and diversity from museum collections makes clear that any additional samples will improve greatly our knowledge of marine biodiversity. Concerted and collaborative efforts are needed to share expertise and limited resources.

Samples collected during these expeditions need to be photographed to document live appearance that would otherwise be lost during preservation. We also need to capture metadata associated with the specimens to be able to understand better the physical characteristics of the habitats for these species. Specimens need to be sub-sampled to create material suitable for genomic analysis. Parts of data acquisition associated with specimens and their biota can be automated and captured digitally directly in the field, speeding up their ingestion in database collections.

>>>>

Similarly, a significant fraction of museum records have missing or inaccurate geographic information associated with them. Geographic information might be available in other forms, but need to be digitized. While tools have been developed to convert names of locales into GPS coordinates on land [@rios2010geolocate], similar approaches need to be develop for the sea.

For both the spelling of scientific names, and the geographic information, computing tools can be developed to detect issues and propose solutions. There are opportunities to develop computing services that use publicly available data to flag and fix these issues directly from collection databases records. It however requires that resources are made available to museum collections in order to address these issues directly in collection databases.

Increasing the computing literacy and teaching data wrangling skills to staff of museums in order for them to manipulate and use the data from their collection database is equally critical. As data across institutions get pooled into the large biodiversity information systems, it is crucial that data standards such as Darwin Core are embraced by the community.

Another venue to improve the quality of the data in biodiversity information systems, is to develop better incitives from journal editors and funding agencies for scientists to publish their occurrence records in databases alongside their papers as it is done for genetic data with GenBank [@Huang2011e].

<!-- Specimens with accurate identifications and specimens that have been preserved in conditions such that it is possible to get DNA out of them should be prioritized, as they yield the most data that are relevant to biodiversity knowledge. -->

@@

This study highlights that we have too little data about too few species of marine invertebrates. We recommend that additional coordinated field expeditions are organized to sample more comprehensively the marine environment. The relation between sampling effort and diversity from museum collections makes clear that any additional samples will improve greatly our knowledge of marine biodiversity. Concerted and collaborative efforts are needed to share expertise and limited resources.

Samples collected during these expeditions need to be photographed to document live appearance that would otherwise be lost during the preservation process. We also need to capture metadata associated with the specimens to be able to understand better the physical characteristics of the habitats for these species. Specimens need to be sub-sampled to create material suitable for genomic analysis. Parts of data acquisition associated with specimens and their biota can be automated and captured digitally directly in the field, speeding up their ingestion in database collections.
